\documentclass{article} % For LaTeX2e
% We will use NIPS submission format
\usepackage{nips13submit_e,times}
% for hyperlinks
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{url}
% For figures
\usepackage{graphicx} 
% math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsopn}
\usepackage{ifthen}
\usepackage{natbib}
\usepackage{caption}
\usepackage{subcaption}

\title{Project-II by Group Rome}
\author{
\fontsize{8}{8}\selectfont{Cimen Gokcen}\\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{gokcen.cimen@epfl.ch}} \\
\And
\fontsize{8}{8}\selectfont{Angelopoulos Vasileios} \\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{vasileios.angelopoulos@epfl.ch}} \\
\And
\fontsize{8}{8}\selectfont{Petrescu Viviana}\\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{viviana.petrescu@epfl.ch}} \\
}

\nipsfinalcopy 

\begin{document}

\maketitle

\begin{abstract}
This report presents experimental results and performance comparison of common machine 
learning methods on two different tasks. The first task is a computer vision problem, a people detection task.
We implemented classifiers that are able to predict to a certain degree if an image contains a standing person or not.
The performance was measured using ROC curves. The second task is a music recommender systems challenge. 
For this problem, we need to predict how many times an user will listen to a certain artist, based on the listening history of this user and the other users. The other subtask of this challenge is to
predict the listening counts of new users, for which we do not have music preference information.
For this, we are given the friendship information with other users for which we already know the listening counts.
The performance of the various method was measured using RMSE.
\end{abstract}

\section{Music Recommendation}
\input{MusicTask}

\section{People Detection}
\input{PeopleTask}

\section*{Acknowledgments}
We would like to thank the course teaching assistants that helped us a lot during this project preparation, not only during the exercise session, but also at their office hours. Furthermore, the help that our teacher Mohammad Emtiyaz Khan offered us was very  important, and we would want to thank him, too. All of the code used and submitted along with this report was written by equally by all of our group members.

\end{document}
